---
title: "09-05 In-class Work - Student"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simulating coin tosses

**Students**: 
- Work alongside the instructor. 

- Complete instructions in **bold** yourself.

- Submit the notebook on Canvas.

---

# Probability through simulations

One of the way to understand probability of an event occurring (for example, probability of getting $k$ heads on $n$ throws) is to **run simulations**.
Then probability of an event can be seen as the proportion/percentage of times that the event occurs in simulations.

Let's simulate coin tosses in R and see if the results of the simulations agree with our computations.
**Tip**: You can always run `?function`, for example `?sample`, in a cell to see what a particular function does and what parameters it takes

```{r coin}
coin <- c("H", "T")
```

Simulate 10 coin tosses using `sample()`:

```{r sample}

```

Find the number of heads:

```{r heads}

```

This is just one simulation. Let's repeat sampling 1000 times:

```{r replicate}

```


If we just care about number of heads, this isn't very convenient or efficient.
Create a function to compute the number of heads in a sample coin toss, and **then** run it 1000 times


```{r simulate}

```


Let's make number of tosses and number of replications into variables so we could compute other quantities for the same scenario.
Let's also store the results of the simulations.

```{r vars}

```

Let's look at how many times we got 2, 30, etc heads:

```{r num_heads}

```

# Visualizing the distribution of head counts

Let's look at the results for all # of heads at once using a histogram:

```{r hist}

```

Default binning sometimes results in bins that don't contain any integer values (for example, `[23.25, 23.75]`), which results in gaps in the histogram because all the values in the data we're plotting (number of heads) are integer. Change `binwidth` to 1 to ensure that every bin contains exactly 1 integer.
 
 
# Simulated vs theoretical probability

**Student: Compute the proportion of simulated tosses with exactly 30 heads**

```{r prop_30}

```

**Student: Use `choose(n,k)` to compute the theoretical probability of getting exactly 30 heads**

```{r theor_30}

```

These numbers are pretty close to each other!

# "At least"

Let's look at all the tosses with at least 30 heads

```{r}

```


**Student: Compute the proportion of simulated tosses with AT LEAST 30 heads**

```{r}

```

**Student: Compute the theoretical probability of getting AT LEAST 30 heads**

```{r}

```

# Unfair coin

Let's simulate an "unfair coin", where the probability of heads is 1/4 instead of 1/2

**Student: Use the `prob` parameter in `sample()` and modify the code to simulate coin tosses with probability of heads 1/4. Plot the histogram of the result.**

```{r}

```

To really see what happens, let's adjust the x axis so that it's from 0 to 50:

```{r}

```

The entire distribution moved to the left -- it's no longer centered around 25.

Let's plot results of the two simulations side by side

```{r}

```  

Not only the distribution shifts to the left, but it also becomes "skinnier" (has less variance). We will return to this when studying the binomial distribution later..

# Conditional probability

**Let's get back to a fair coin. Simulate the conditional probability of having _exactly 2_ heads in 10 fair coin tosses, given that there has _at least one head_.**

*Hint*: first, do the simulations as before; then, restrict the sample space 

```{r}

```

**Compute the theoretical probability of having exactly 2 heads in 10 fair coin tosses, given that there has at least one head.**

```{r}

```